% CS305 HW4

\documentclass{article}
\usepackage{anysize}
\usepackage{wasysym}
\usepackage{graphicx}

\marginsize{2cm}{2cm}{2cm}{2cm}

\title{CS305 HW4}
\author{Russell Miller}
\date{\today}

\begin{document}

\maketitle

\paragraph{1. Visit the TRUSTe website and summarize important requirements 
TRUSTe sites must meet for protecting your web and e-mail privacy.\\}
Your site must manage user data per specific rules, and must state those rules in
a privacy policy printed on your site. You must manage users' privacy complaints.
You must encrypt sensitive data.\\
\\
For e-mail you must allow users to opt-out of subscriptions and personal info
sharing. They must also have a way to unsubscribe.

\paragraph{2. Find a shopping site that has its own privacy policy.}
\begin{verbatim}
https://shirt.woot.com/user/privacynotice.aspx
\end{verbatim}
First of all, you can see via the URL that Woot uses HTTPS. This is a protocol 
which encrypts information that is sent, as TRUSTe requires. Also, as TRUSTe 
outlines, Woot details the information that they are gathering and exactly what they 
are using it for. They have an intuitive interface for changing personal information
on your account, and at the end of the privacy policy is an e-mail dedicated to
handling privacy issues that users have.\\
\\
In this relatively short privacy policy I don't see anything that contradicts TRUSTe.
Woot, however, does not have a service attached where complaints can be filed.
Everything is handled internally. However, I've personally contacted their customer 
service and they do a fantastic job.

\end{document}