% CS305 HW1

\documentclass{article}
\usepackage{anysize}
\usepackage{wasysym}
\usepackage{graphicx}

\marginsize{2cm}{2cm}{2cm}{2cm}

\title{CS305 HW1}
\author{Russell Miller}
\date{\today}

\begin{document}

\maketitle

\section{Examples of Computer Science Organizations\\ with a Code of Ethics}

\begin{enumerate}
\item Association for Computing Machinery\\
http://www.acm.org/about/code-of-ethics
\item Institute of Electrical and Electronics Engineers\\
http://www.ieee.org/about/corporate/governance/p7-8.html
\item Computing Research and Education Association of Australasia\\
http://core.edu.au/index.php/page/code-of-conduct
\end{enumerate}

\section{Another Industry's Code of Ethics}

Portland Police\\
http://www.portofportland.com/police\_mission.aspx

\section{Compare and Contrast}
Honesty is a major theme. 
For the IEEE it was point 3: ``to be honest and realistic in stating claims or estimates based on available data.''
For the ACM it was point 1.3: ``Be honest and trustworthy.''
For the CORE it was covered in multiple statements. ``Confidentiality must be observed.'' 
``Supervisors should ensure that the work submitted by research students is the work of the student.''
For the Portland Police it was their first value listed - integrity.\\
\\
Professionalism is another one seen across all of these organizations.
The IEEE doesn't explicitly state professionalism as a goal, however many of the goals listed fall under that theme.
Avoiding conflicts of interest, maintaining competence and fully disclosing limitations, fair treatment, and assisting colleagues
should all be considered acts of professionalism. All of the other organizations explicitly stated a need for professionalism.\\
\\
Self-improvement is common among all of them. It fell under professionalism and teamwork for the Portland Police.
It was point 10 for the IEEE. The ACM states that ``excellence is perhaps the most important obligation of a professional.''
The CORE doesn't seem to cover this topic, but because they focus entirely on research their main focuses are confidentiality and proper citation.\\
\\
The Portland Police do not specifically mention criticism as an avenue for self-improvement, whereas for the IEEE it is point 7.
For the ACM it is point 2.4. For the CORE it is not mentioned, however the research students do have a supervisor who must approve their work.

\pagebreak

\section{Guidelines from a Professional}
Laura Bloom - Business Ethics Speaker and Consultant\\ 
http://www.thebusinessethicsblog.com/\\
By searching around the site I found this: http://www.thebusinessethicsblog.com/your-code-of-ethics-shouldnt-be-just-window-dressing\\
and this: http://www.thebusinessethicsblog.com/write-your-rules-with-care\\

\section{An Organization with Resources for\\
Reporting Ethical Violations}
American Psychological Association - Whistleblower Protection\\
http://www.apa.org/about/division/officers/whistleblower.aspx

\end{document}