% CS305 HW3
% Russell Miller

\documentclass{article}
\usepackage{anysize}
\usepackage{wasysym}
\usepackage{graphicx}

\marginsize{2cm}{2cm}{2cm}{2cm}

\title{CS305 HW3}
\author{Russell Miller}
\date{\today}

\begin{document}

\maketitle

\paragraph{1. Find a URL for a patent violation case that was contested, 
which appeared in the last 5 years and where a penalty was assessed.}
\begin{verbatim}
http://tech.fortune.cnn.com/2011/07/16/apple-vs-google-inside-an-android-patent-violation/
\end{verbatim}
There is a smart phone function that allows phone numbers, e-mail addresses, 
web links, and street addresses to be clickable in messages. Apple claims that 
Android phones are in violation of their patent. It's U.S. Patent No. 5,946,647 
and HTC was found guilty of violating it. They make Android devices.\\
\\
HTC filed for an appeal, but if this decision holds the International Trade 
Commission could ban the importing of HTC Android devices.

\paragraph{2. Find a URL for a patent case where the patent was found to be invalid.}
\begin{verbatim}
http://www.nytimes.com/2007/05/01/business/01bizcourt.html
\end{verbatim}
This case was originally covering the use of an electronic sensor which allowed
a vehicle's computer to link to a gas pedal. It was ruled invalid because this link
is considered an ``obvious'' innovation. The district court ruled it so, but the Court of 
Appeals for the Federal Circuit reversed it. When it reached the Supreme Court it
was reversed again, in favor of the argument that this innovation was ``obvious.''

\paragraph{3. Find a case in the last 5 years where copying a program, for commercial use, 
was ruled fair use.}
\begin{verbatim}
https://www.eff.org/deeplinks/2006/02/perfect-10-v-google-more-smooth-crunchy
\end{verbatim}
The copying in this case is image content of adult website Perfect 10 by Google's image search
thumbnails.
One of the factors of fair use is purpose and character. The court saw that Google's search
engine was beneficial for the general public and therefore took that into consideration more than
the benefit of Google or Perfect 10. Another factor is effect upon work's value. This came into
consideration because of Google's AdSense revenue in relation to the links in question. To
attempt to help their case, Perfect 10 signed an agreement with a company called Fonestarz.
However, they did so after suing Google. Therefore, this argument was moot. One of the silliest
points Perfect 10 tried to bring to court was that Google needed to ``supervise or control'' the
websites that were linked in its search results. It's no surprise that the court threw Perfect 10's case
out.\\

\end{document}
